Supplemental data to ``\emph{k}-mer-based GWAS enhances causal variant and candidate gene discovery in soybean''

### 2023-02-28 additional_files/additional_file_1.tex
Remove vg results from table S11 (signals table)

		\begin{TableNotes}
		\item[a] Most significant -log\textsubscript{10}(\emph{p}) previously reported at this locus by the study in the Study column
		\item[b] Gene associated with the locus. A question mark following the identifier of the gene indicates that this is simply a candidate
			that has yet to be confirmed. A dash indicates that no candidate has been suggested yet. We have only included candidate
			genes that have been suggested in previous studies.
		\item[c] Most significant -log\textsubscript{10}(\emph{p}) reported by Platypus at this locus. A dash indicates that no signal
			was detected by Platypus at this locus. The same applies for other methods (vg, Paragraph, \emph{k}-mers) in
			their respective columns.
		\item[d] The \emph{p}-value at the W1 locus using the \emph{k}-mers method was so small that it was numerically equal
			to zero. This value was therefore set to the -log\textsubscript{10} of the smallest value that could be represented
			in R using our machine.
		\end{TableNotes}

		\begin{longtable}{llcclccccl}

			\caption[Description of loci associated with the traits studied]%
			{Description of loci associated with the traits studied and -log\textsubscript{10}(\emph{p}) of significant
			signals detected in our study using four different genotypic datasets (Platypus, vg, Paragraph, \emph{k}-mers).}\\
			\label{signals_table}\\

			\toprule
			Trait & Locus & Chromosome & -log\textsubscript{10}(\emph{p})\tnote{a} & Gene\tnote{b} & Platypus\tnote{c} & vg & Paragraph & \emph{k}-mers  & Study \\
			\midrule \endfirsthead

@@

			\toprule
			Trait & Locus & Chromosome & -log10(p) & Gene & Platypus & vg & Paragraph & k-mers  & Study \\
			\midrule
			\endhead

@@

			\bottomrule \insertTableNotes
			\endlastfoot
			\csvreader[head to column names,
			late after line=\\,
			late after last line=,
			before reading={\catcode`\#=12},
			after reading={\catcode`\#=6},
			/csv/separator=semicolon]%
			{../tables/signals_table.csv}{}{\Trait & \Locus & \Chromosome & \Pvalues & \Gene & \Platypus & \Vg & \Paragraph & \Kmers & \Study}

>>>>

		\begin{TableNotes}
		\item[a] Most significant -log\textsubscript{10}(\emph{p}) previously reported at this locus by the study in the Study column
		\item[b] Gene associated with the locus. A question mark following the identifier of the gene indicates that this is simply a candidate
			that has yet to be confirmed. A dash indicates that no candidate has been suggested yet. We have only included candidate
			genes that have been suggested in previous studies.
		\item[c] Most significant -log\textsubscript{10}(\emph{p}) reported by Platypus at this locus. A dash indicates that no signal
			was detected by Platypus at this locus. The same applies for other methods (Paragraph, \emph{k}-mers) in
			their respective columns.
		\item[d] The \emph{p}-value at the W1 locus using the \emph{k}-mers method was so small that it was numerically equal
			to zero. This value was therefore set to the -log\textsubscript{10} of the smallest value that could be represented
			in R using our machine.
		\end{TableNotes}

		\begin{longtable}{llcclcccl}

			\caption[Description of loci associated with the traits studied]%
			{Description of loci associated with the traits studied and -log\textsubscript{10}(\emph{p}) of significant
			signals detected in our study using four different genotypic datasets (Platypus, Paragraph, \emph{k}-mers).}\\
			\label{signals_table}\\

			\toprule
			Trait & Locus & Chromosome & -log\textsubscript{10}(\emph{p})\tnote{a} & Gene\tnote{b} & Platypus\tnote{c} & Paragraph & \emph{k}-mers  & Study \\
			\midrule \endfirsthead

@@

			\toprule
			Trait & Locus & Chromosome & -log10(p) & Gene & Platypus & Paragraph & k-mers  & Study \\
			\midrule
			\endhead

@@

			\bottomrule \insertTableNotes
			\endlastfoot
			\csvreader[head to column names,
			late after line=\\,
			late after last line=,
			before reading={\catcode`\#=12},
			after reading={\catcode`\#=6},
			/csv/separator=semicolon]%
			{../tables/signals_table.csv}{}{\Trait & \Locus & \Chromosome & \Pvalues & \Gene & \Platypus & \Paragraph & \Kmers & \Study}
